Hydras, Ordinals \& Co. \\ A library in Coq of entertaining formal mathematics

### 2021-10-12 doc/JFLA2022/paper.tex
small pass over monorepo

In the context of Coq projects, they did not use to be well-supported.
%
One of the only monorepo in the Coq ecosystem was the math-comp repository, and it used a custom build infrastructure to make this possible.
%
However, recent improvements in tooling have made their use possible, and therefore we have used them more and more, for instance within \community.

>>>>

In the context of Coq projects, they did not use to be well-supported.
%
One of the few early monorepos in the Coq ecosystem was the Mathematical Components (math-comp) repository, which used a custom build infrastructure to check multiple packages on each commit.
%
However, recent improvements in tooling have made their use easier, and therefore we have used them more and more, for instance within \community.
